### 2024-01-13 documentation/thesis/thesis_document.tex
more thesis

Low-field magnetic resonance imaging (low-field \gls{mri}) is a
\gls{mri} technique that operates at a lower magnetic field strength
compared to conventional high-field \gls{mri} scanners. Typically, the
magnetic field in low-field MRI systems between
\passthrough{\lstinline!0.1T!} and \passthrough{\lstinline!0.3T!}
compared to the usual \passthrough{\lstinline!1.5T!} to
\passthrough{\lstinline!3T!} in high-field \gls{mri}
scanners.\cite{Hori2021-pt}

@@

Der Shimming-Prozess ist ein entscheidender Schritt bei der
Magnetresonanztomographie (MRT), um homogene Magnetfelder für präzise
Bildgebung zu gewährleisten. Shimming korrigiert Unregelmäßigkeiten im
statischen Magnetfeld, die durch äußere Einflüsse oder interne
Systemfehler entstehen können. Dieser Prozess optimiert die
Feldhomogenität, was für hochauflösende und artefaktfreie Bilder
entscheidend ist.

Die Quellen für den Shimming-Prozess können Hardware- und
Software-basiert sein. Hardware-Shimming beinhaltet den Einsatz von
Gradienten- und Radiofrequenzspulen, die gezielt platziert werden, um
das Magnetfeld auszurichten. Software-Shimming hingegen verwendet
Algorithmen, um die Steuerparameter des MRT-Systems anzupassen und die
Homogenität zu verbessern.

Forschungspublikationen wie ``Shimming Techniques in Magnetic Resonance
Imaging'' (DOI: 10.1007/978-1-4939-2815-6\_3) bieten detaillierte
Einblicke in verschiedene Shimming-Methoden und Techniken. Diese
Fortschritte in der Shimming-Technologie tragen dazu bei, die
diagnostische Genauigkeit und Bildqualität in der MRT erheblich zu
verbessern.

>>>>

Low-field magnetic resonance imaging (low-field \gls{mri}) is a
\gls{mri} technique that operates at a lower magnetic field strength
compared to conventional high-field \gls{mri} scanners. Typically, the
magnetic field in low-field MRI systems between
\passthrough{\lstinline!0.1T!} and \passthrough{\lstinline!0.3T!}
compared to the usual \passthrough{\lstinline!1.5T!} to
\passthrough{\lstinline!3T!} and above in high-field \gls{mri}
scanners.\cite{Hori2021-pt}

@@

The shimming process is a crucial step in magnetic resonance imaging
\gls{mri} to ensure homogeneous magnetic fields for precise imaging.
Shimming corrects irregularities in the static magnetic field that can
be caused by external influences or internal system errors. This process
optimizes field homogeneity, which is crucial for high-resolution and
artifact-free images.\cite{10.3389/fphy.2021.704566}

The sources for the shimming process can be hardware and software based.
Hardware shimming involves the use of gradient and radio frequency coils
that are specifically placed to align the magnetic field. Software
shimming, on the other hand, uses algorithms to adjust the control
parameters of the \gls{mri} system and improve
homogeneity.\cite{10.3389/fphy.2021.704566}
